Reviewer Comments (Scientific Reports)

### 2020-03-20 notebook/ms.Rmd
Fix the hyphenations of food webs to make things consistent
Add a sentence to the MS to address Reviewer 1's comment 3

Cascade food-webs were constructed following Solow and Beet [@Solow1998]. First, a random matrix $\mathbf{A}$ was generated with off-diagonal elements sampled i.i.d so that $A_{ij} \sim \mathcal{N}(0, 0.4)$. Each component in the system was ranked from $1$ to $S$. If component $i$ had a higher rank than component $j$ and $A_{ij} < 0$, then $A_{ij}$ was multiplied by $-1$. If $i$ had a lower rank than $j$ and $A_{ji} < 0$, then $A_{ji}$ was multiplied by $-1$. In practice, this resulted in a matrix $\mathbf{A}$ with negative and positive values in the lower and upper triangles, respectively. Diagonal elements of $\mathbf{A}$ were set to $-1$ and $C = 1$. I simulated cascade food webs across all combinations of $S = \{2, 3, ..., 59, 60\}$.

@@

**Figure 4: Stability of large complex systems with and without variation in component response rate ($\boldsymbol{\gamma}$).** The $\ln$ number of systems that are stable across different system sizes ($S = \{2, 3, ..., 49, 50 \}$) given $C = 1$, and the proportion of systems for which variation in $\gamma$ is critical for system stability. For each $S$, 1 million complex systems are randomly generated. Stability of each complex system is tested given variation in $\gamma$ by randomly sampling $\gamma \sim \mathcal{U}(0, 2)$. Stability given $\sigma^{2}_{\gamma}>0$ is then compared to stability in an otherwise identical system in which $\gamma = E[\mathcal{U}(0, 2)]$ for all components. Blue and red bars show the number of stable systems in the absence and presence of $\sigma^{2}_{\gamma}$, respectively. The black line shows the proportion of systems that are stable when $\sigma^{2}_{\gamma}>0$, but would be unstable if $\sigma^{2}_{\gamma}=0$.

>>>>

Cascade food webs were constructed following Solow and Beet [@Solow1998]. First, a random matrix $\mathbf{A}$ was generated with off-diagonal elements sampled i.i.d so that $A_{ij} \sim \mathcal{N}(0, 0.4)$. Each component in the system was ranked from $1$ to $S$. If component $i$ had a higher rank than component $j$ and $A_{ij} < 0$, then $A_{ij}$ was multiplied by $-1$. If $i$ had a lower rank than $j$ and $A_{ji} < 0$, then $A_{ji}$ was multiplied by $-1$. In practice, this resulted in a matrix $\mathbf{A}$ with negative and positive values in the lower and upper triangles, respectively. Diagonal elements of $\mathbf{A}$ were set to $-1$ and $C = 1$. I simulated cascade food webs across all combinations of $S = \{2, 3, ..., 59, 60\}$.

@@

**Figure 4: Stability of large complex systems with and without variation in component response rate ($\boldsymbol{\gamma}$).** The $\ln$ number of systems that are stable across different system sizes ($S = \{2, 3, ..., 49, 50 \}$) given $C = 1$, and the proportion of systems for which variation in $\gamma$ is critical for system stability. For each $S$, 1 million complex systems are randomly generated. Stability of each complex system is tested given variation in $\gamma$ by randomly sampling $\gamma \sim \mathcal{U}(0, 2)$. Stability given $\sigma^{2}_{\gamma}>0$ is then compared to stability in an otherwise identical system in which $\gamma = E[\mathcal{U}(0, 2)]$ for all components. Blue and red bars show the number of stable systems in the absence and presence of $\sigma^{2}_{\gamma}$, respectively. The black line shows the proportion of systems that are stable when $\sigma^{2}_{\gamma}>0$, but would be unstable if $\sigma^{2}_{\gamma}=0$ (i.e., the conditional probability that $\mathbf{A}$ is unstable given that $\mathbf{M}$ is stable).

### 2020-03-20 notebook/sci_rep_reviews.Rmd
Add a sentence to the MS to address Reviewer 1's comment 3

Reviewer 1 is correct that the line illustrates the conditional probability that $A$ is unstable given that $\gamma A$ is stable. In other words, the proportion of complex systems found to be stable, but which would have been unstable if it were not for the variation in component response rates.

I have explained the result shown by the black line of Figures 3 and 4 now more clearly in my revision (line XXX).

>>>>

Reviewer 1 is correct that the line illustrates the conditional probability that $A$ is unstable given that $M = \gamma A$ is stable. In other words, the proportion of complex systems found to be stable, but which would have been unstable if it were not for the variation in component response rates.

I have explained the result shown by the black line of Figures 3 (now 4), and the former figure 4 (now in the SI), now more clearly in my revision (line XXX).
